SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-08 docs/questioning.tex
more work on the analysis section

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2},
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

@@

Table~\ref{tab:comp} indicates that 27 out of
34 mechanisms were tested on real-world applications
known to be vulnerable. The vulnerabilities
associated with these applications are enlisted
in the following providers: the Common Vulnerabilities
and Exposures ({\sc cve})
database,\footnote{\url{https://cve.mitre.org/}}
the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
security mailing list, the
{\sc xss}ed.com\footnote{\url{www.xssed.com}}
security bulletin provider, Microsoft's security
bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
and the ha.ckers.org\footnote{\url{www.xssed.com}}
security bulletin provider. Figure~\ref{fig:defect_sources}
presents how many (in terms of percentages) and which
(in the figure's caption) authors referred to which source.
In numerous occassions authors performed tests based
on the same applications. For example, 12 mechanisms
were tested on a vulnerable version of
{\sc phpbb}.\footnote{https://www.phpbb.com/}

@@

\section{Discussion}

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2},
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos D. Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

Here we comment on how the mechanisms that we
described earlier, were tested in terms of both
diagnostic and computational performance.

@@

Table~\ref{tab:comp} indicates that the authors of 3 out of 34
({\bf 8.8\%}) publications, provided complete quadruples.
On the other hand, we see that 4 out of
34 ({\bf 11.7\%}) were not tested at all
in terms of diagnostic performance. In this cases,
all the four elements of the quadruples are not
available ({\sc na}).
% Maybe we should comment on the fact that these are
% frameworks coming from the etiological category
% and detect the attacks ``by design".
An interesting observation is that 10 out of 34
({\bf 29.41\%}) of the authors performed only attacks
during their tests and did not test their mechanisms
to see if they produce any false alarms. The corresponding
quadruples in this case, are the ones that contain {\sc tp} and
{\sc fn} results but {\sc tn} and {\sc fp} results are not
available ({\sc na}). This stresses the fact that authors
of these mechanisms were more interested to make sure that
their mechanisms can detect known attacks than to see how
they respond under normal conditions.
In some occasions (where the number of {\sc tp} results
are not quantified), authors did not mention how many or
which attacks they performed.
Moreover, we observe in some cases, that even if
the authors report the existence of possible
false positive and negative results, they have not
quantified them ({\sc nq}).

Furthermore, we see that 27 out of
34 mechanisms were tested on real-world applications
known to be vulnerable. The vulnerabilities
associated with these applications are enlisted
in the following providers: the Common Vulnerabilities
and Exposures ({\sc cve})
database,\footnote{\url{https://cve.mitre.org/}}
the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
security mailing list, the
{\sc xss}ed.com\footnote{\url{www.xssed.com}}
security bulletin provider, Microsoft's security
bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
and the ha.ckers.org\footnote{\url{www.xssed.com}}
security bulletin provider. Figure~\ref{fig:defect_sources}
presents how many (in terms of percentages) and which
(in the figure's caption) authors referred to which source.
In numerous occassions authors performed tests based
on the same applications. For example, 12 mechanisms
were tested on a vulnerable version of
{\sc phpbb}.\footnote{https://www.phpbb.com/}

@@

Our first observation indicates that only 6
out of 34 ({\bf 17.6\%}) of the authors provided a homepage for
their mechanism through their publication.
2 from these 6 homepages are currently not available.
Also, in 5 cases, authors made either the source code
or their executables available after their paper
got published. Finally, we observe that only 3
out of 34 ({\bf 8.8\%}) authors have currently
their testbeds available on-line.

\section{Discussion and Lessons Learned}

Our findings indicate that currently, the testing of
the diagnostic performance of
mechanisms that detect top web application attacks
has not a standard form. In addition,
there are many mechanisms that are tested in a poor manner.

A reasonable argument would be that many
mechanisms (especially the ones coming from the
etiological category), do not need to be established
purely through testing since they provide systematic
arguments as to why their design is secure against attacks.
However, their implementations are not always efficient
and as we observed they can be circumvented.
